---
title: "Diagnostic plots for the LEEF-2 RRD `r params$db`"
author: "Rainer M Krug"
date: | 
  | Last `timestamp`: `r LEEF.analysis::read_sql(params$db, sql = 'SELECT MAX(timestamp) FROM density WHERE timestamp < 30000000')`
  | Sampling `day`: `r LEEF.analysis::read_sql(params$db, sql = 'SELECT MAX(day) FROM density WHERE day < 1000')`
  | `LEEF.analysis` package version: `r packageVersion('LEEF.analysis')`
output:
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: hide
    embed-resources: true
  pdf_document:
    dev: pdf
    fig_width: 10
    fig_height: 12
  word_document: 
    dev: png
    fig_width: 10
    fig_height: 12
params:
  db: ~/Desktop/9.backend/LEEF-2.RRD.sqlite
  lastDays: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LEEF.analysis)
```
## Invocation from commandline
The report can be generated from the command line by using

```{bash info_invocation, eval = FALSE}
Rscript -e "library(LEEF.analysis); LEEF_2_report_diagnostic(db = 'DATABASE PATH',  template = 'LEEF_2', format = 'html', lastDays = 7);"
```

\pagebreak

## Response  variable in the last timestap

```{r response_per_timestamp, fig.height = 26}
LEEF_2_plot_response_incubator(params$db)
```

\pagebreak

## Check Bottles per Measurement per Timestep

This plot shows, if a `bottle` is present for the `measurement` for the timestamps analysed. Each `measurement` is a panes. Missing dots indicate missing datapoints for the `bottle` at the `measurement` for the `timestamp`.

```{r bottles_per_timestamp}
LEEF_2_plot_bottles_per_timestamp(params$db, lastDays = params$lastDays)
```

\pagebreak

## Density of Species per bottle as measured by measurement over time

\pagebreak

### Bemovi Magnification 16
```{r dens_species_b_16_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "bemovi_mag_16",
  species_set_id = NULL
)
```

\pagebreak

### Bemovi Magnification 25
```{r dens_species_b_25_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "bemovi_mag_25",
  species_set_id = NULL
)
```

\pagebreak

### Bemovi Magnification 25 cropped
```{r dens_species_b_25_crop_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "bemovi_mag_25_cropped",
  species_set_id = NULL
)
```

\pagebreak

### Flowcam Everything
```{r dens_species_fcam_all_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "flowcam",
  species_set_id = NULL
)
```

\pagebreak

### Flowcam Algae
```{r dens_species_fcam_al_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "flowcam",
  species_set_id = "LEEF_2_flowcam_algae"
)
```
`
\pagebreak

### Flowcam Rest
```{r dens_species_fcam_rest_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "flowcam",
  species_set_id = "LEEF_2_flowcam_rest"
)
```


\pagebreak

### Flowcytometer
```{r dens_species_fcyt_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "flowcytometer",
  species_set_id = NULL
)
```

\pagebreak

### Manualcount
```{r dens_species_mc_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = FALSE, 
  measurement = "manualcount",
  species_set_id = NULL
)
```

\pagebreak

### Percent O~2~

```{r percent_o2_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_o2s_per_bottle_per_timestamp(
  params$db
)
```

\pagebreak

### Conductivity

```{r conductivity_raw, fig.height = 10, fig.width = 15}
LEEF_2_plot_conductivity_per_bottle_per_timestamp(
  params$db
)
```

\pagebreak

### TOC and TC

```{r toc_raw_1_1, fig.height = 10, fig.width = 15}
LEEF_2_plot_tocs_per_bottle_per_timestamp(
  params$db,
  type = c("TOC", "TC")
)
```

\pagebreak

### IC and TN


```{r toc_raw_2_1, fig.height = 10, fig.width = 15}
LEEF_2_plot_tocs_per_bottle_per_timestamp(
  params$db,
  type = c("IC", "TN")
)
```

## 4^th^ root Density of Species per bottle as measured by measurement over time

\pagebreak

### Bemovi Magnification 16
```{r dens_species_b_16, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "bemovi_mag_16",
  species_set_id = NULL
)
```

\pagebreak

### Bemovi Magnification 25
```{r dens_species_b_25, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "bemovi_mag_25",
  species_set_id = NULL
)
```

\pagebreak

### Bemovi Magnification 25 cropped
```{r dens_species_b_25_crop, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "bemovi_mag_25_cropped",
  species_set_id = NULL
)
```

\pagebreak

### Flowcam Algae
```{r dens_species_fcam_al, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "flowcam",
  species_set_id = "LEEF_2_flowcam_algae"
)
```

\pagebreak

### Flowcam Rest
```{r dens_species_fcam_rest, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "flowcam",
  species_set_id = "LEEF_flowcam_rest"
)
```


\pagebreak

### Flowcytometer
```{r dens_species_fcyt, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "flowcytometer",
  species_set_id = NULL
)
```

\pagebreak

### Manualcount
```{r dens_species_mc, fig.height = 10, fig.width = 15}
LEEF_2_plot_density_species_per_bottle_per_timestamp(
  params$db, 
  transform_density_4throot = TRUE, 
  measurement = "manualcount",
  species_set_id = NULL
)
```

\pagebreak

### Percent O~2~

```{r percent_o2, fig.height = 10, fig.width = 15}
LEEF_2_plot_o2s_per_bottle_per_timestamp(
  params$db
)
```

\pagebreak

### Conductivity

```{r conductivity, fig.height = 10, fig.width = 15}
LEEF_2_plot_conductivity_per_bottle_per_timestamp(
  params$db
)
```

\pagebreak

### TOC and TC

```{r toc_raw_1_2, fig.height = 10, fig.width = 15}
LEEF_2_plot_tocs_per_bottle_per_timestamp(
  params$db,
  type = c("TOC", "TC")
)
```

\pagebreak

### IC and TN


```{r toc_raw_2_2, fig.height = 10, fig.width = 15}
LEEF_2_plot_tocs_per_bottle_per_timestamp(
  params$db,
  type = c("IC", "TN")
)
```
