---
title: "Check of final RRD"
author: "Rainer M Krug"

format:
  html:
    toc: true
    toc-expand: 2
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
---

```{r}
#| label: setup
#| 

library(tidyverse)
library(patchwork)
## Get the LEEF analysis package
# drat::addRepo("LEEF-UZH")
# install.packages("bemovi.LEEF")
# install.packages("LEEF.measurements.flowcam")
# options(repos = c(
#   leefuzh = 'https://leef-uzh.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# # Download and install LEEF.analysis in R
# install.packages('LEEF.analysis')
library(LEEF.analysis)
library(DBI)
library(RSQLite)
library(data.table)
library(pracma)
library(parallel)
library(doParallel)
library(here)

set.seed(1)
options(dplyr.summarise.inform = FALSE)

options(RRDdb = "/Volumes/RRD.Reclassification_final/LEEF.RRD.v1.8.5_final.sqlite")
# options(RRDdb = "/Volumes/RRD.Reclassification_final/LEEF.RRD.v1.8.5_2.sqlite")

# options(RRDdb = "LEEF.RRD.v1.8.5_4.sqlite")

densities <- db_read_table(table = "density") %>%
  collect() %>%
  arrange(day)

# CHECK: Code in previous 3 lines give the below message, which seems indicate a problem in the data
# Column `biomass`: mixed type, first seen values of type real, coercing other values of type string
# RMK: OK

o2 <- db_read_table(table = "o2") %>% collect()

water_chem <- db_read_toc() %>% collect()

```

## &#10003; check that all variables are (species) present
CHECK: Must be TRUE

```{r}

vars <- c(
  "Coleps sp.", "Paramecium bursaria", "Paramecium caudatum",
  "Stylonychia sp.", "Colpidium striatum", "Euplotes daidaleos",
  "Dexiostoma campylum", "Loxocephalus sp.", "Chlamydomonas reinhardtii",
  "Chlamydomonas clumps", "Cosmarium botrytis", "Debris",
  "Desmodesmus armatus", "Desmodesmus clumps", "Digested algae",
  "Dividing Chlamydomonas", "Small cells", "Small unidentified",
  "Staurastrum gracile", "Colpidium vacuoles", "Monoraphidium obtusum",
  "Staurastrum polytrichum", "Didinium nasutum",
  "Bacteria", "Algae"
)


all(vars %in% unique(densities$species)) 
idx <- unique(densities$species) %in% vars
idx

```
RMK: OK

## &#10003; check that there are no additional variables
CHECK: must be empty
```{r}


unique(densities$species)[!idx]


# table(densities$species, densities$measurement)/123 # dividing by 123 should give an integer value (the number of bottles). Not a valid criterion for all measurements

```
RMK: OK

## Next check: missing timestamps
### &#10003; length
CHECK: length should be 123

```{r}

timestamps <- unique(densities$timestamp)
length(timestamps)


```
RMK: OK


### &#10003; more detailed per measurement and bottle

CHECK: The following data.frame should be empty

```{r}

missing_timestamps <- densities %>%
  group_by(measurement, species, bottle) %>%
  reframe(missing_timestamps = as.numeric(timestamps[which(!(timestamps %in% unique(timestamp)))])) %>%
  dplyr::filter(
    measurement != "manualcount",
    !(measurement == "bemovi_mag_25_non_cropped" & missing_timestamps < 20211103), # non_cropped only used from 20211103 onwards
    !(measurement == "flowcytometer" & (missing_timestamps %in% c(20220404, 20220406, 20220415, 20220418, 20220425))) # For the flowcytometer for the following timestamps there was no data collection: "20220404" "20220406" "20220415" "20220418" "20220425"
  )
missing_timestamps
## TODO RMK: flowcam Strrastum is missing
missing_timestamps$measurement |>
    unique() |>
    sort()
missing_timestamps$missing_timestamps |>
    unique() |>
    sort()
missing_timestamps$species |>
    unique() |>
    sort()
missing_timestamps$bottle |>
    unique() |>
    sort()

missing_timestamps |>
    arrange(missing_timestamps, bottle) |>
    knitr::kable()

```


### &#10003; missing timetamps oxygen

CHECK: The following data.frame should be empty

The measurement `4 b_29 20211004` is missing in the raw data.

```{r}


missing_timestamps_o2 <- o2 %>%
  group_by(sensor, bottle) %>%
  summarize(missing_timestamps = as.numeric(timestamps[which(!(timestamps %in% unique(timestamp)))])) %>%
  dplyr::filter(!(missing_timestamps==20211208 & bottle=="b_01" & sensor==4),
                missing_timestamps!=20211201,
                ) # Previously confirmed missing data is filtered out
missing_timestamps_o2

```
RMK: OK b_29 Sensor 4 is mssing in raw data

### &#10003; missing timetamps water chemistry

CHECK: The following data.frame should be empty

```{r}

# This check fails (missing_timestamps_wc). Romana confirmed that there is raw data for timestamps 20211001 and 20220624 (note: date is incorrect specified in 20211001 water chem file). Because of this I'm assuming that the other timestamps should also be present (most of them were in previous RRD versions). Please check.
# 
missing_timestamps_wc <- water_chem %>%
  group_by(type, bottle) %>%
  summarize(missing_timestamps = as.numeric(timestamps[which(!(timestamps %in% unique(timestamp)))])) 
table(missing_timestamps_wc$missing_timestamps, missing_timestamps_wc$bottle) |>
    knitr::kable()
missing_timestamps_wc |>
    knitr::kable()
```
RMK: OK: these missing timestamps are because of the filtering out of `!is.na(conc)` in the detrending. They were left in, because they either had one measurement ur the the CV was larger than the threashold in all measurements. The missing timestamps are therefore not a problem.

## &#10003; Check NAs

### &#10003; NAs in density
CHECK: The following data.frame should be empty

```{r}

NAs <- densities %>%
  dplyr::filter(species!="Debris", species!="Digested algae",species!="Small unidentified",species!="Colpidium vacuoles", species!="Didinium nasutum", species != "Algae") %>% #biomass not calculated for these classes
  group_by(measurement, species, bottle, timestamp) %>%
  summarize(densityNA = sum(is.na(density)),
            biomassNA = sum(is.na(biomass))) %>%
  dplyr::filter(biomassNA>0 | densityNA>0,
                !(measurement %in% c("bemovi_mag_25","bemovi_mag_25_cropped","bemovi_mag_25_non_cropped") & densityNA == 1)) # There is 1 NA for all species for all bottles at magnification 25 (20220622 missing)
NAs

```
TODO RMK flowcam


### &#10003; NAs in Oxygen

CHECK: The following data.frame should be empty

```{r}

NAs_o2 <- o2 %>%
  group_by(sensor, bottle) %>%
  summarize(o2NA = sum(is.na(percent_o2))) %>%
  dplyr::filter(o2NA>0)
NAs_o2

```
RMK: OK

### &#10003; NAs in water chemistry

CHECK: The following data.frame should be empty

```{r}

NAs_wc <- water_chem %>%
  group_by(type, bottle) %>%
  summarize(concentrationNA = sum(is.na(concentration))) %>%
  dplyr::filter(concentrationNA>0)
NAs_wc

# RMK: OK

```
## &#10003; Check if all species present in all the bottles they are supposed to be

see below for check
all uncommented checks below were passing at 4pm on 14.6.2023 while using LEEF.RRD.v1.8.5_4.sqlite
RMK: OK

### preparation
```{r}

## TO FIX...
comps <- db_read_table(table = "composition") %>% collect() # still has the old species names... FIXED
design <- db_read_table(table = "experimental_design") %>% collect()

design <- full_join(design, comps)

design_long <- design %>%
  pivot_longer(cols = -c(bottle,temperature,richness,composition,incubator), names_to = "species") %>%
  dplyr::filter(value == 1) %>%
  select(-value)

design_long <- design_long %>%
  mutate(species = case_when(species == "Chlamydomonas" ~ "Chlamydomonas reinhardtii",
                             species == "Cosmarium" ~ "Cosmarium botrytis",
                             species == "Desmodesmus" ~ "Desmodesmus armatus",
                             species == "Tetrahymena" ~ "Tetrahymena thermophila",
                             species == "Loxocephallus" ~ "Loxocephalus sp.",
                             species == "Paramecium_caudatum" ~ "Paramecium caudatum",
                             species == "Coleps_irchel" ~ "Coleps sp.",
                             species == "Paramecium_bursaria" ~ "Paramecium bursaria", 
                             species == "Didinium" ~ "Didinium nasutum",
                             species == "Staurastrum1" ~ "Staurastrum gracile",
                             species == "Euplotes" ~ "Euplotes daidaleos",
                             species == "Colpidium" ~ "Colpidium striatum",
                             species == "Stylonychia2" ~  "Stylonychia sp.",
                             species == "Monoraphidium" ~ "Monoraphidium obtusum",
                             species == "Staurastrum2" ~ "Staurastrum polytrichum",
                             species == "Stylonychia1" ~ "Stylonychia mytilus",
                             species == "Dexiostoma" ~ "Dexiostoma campylum",
                             species == "Cryptomonas" ~ "Cryptomonas sp.")
  ) %>%
  dplyr::filter(species != "Cryptomonas sp.", species != "Stylonychia mytilus")

bottles <- c("b_30", "b_02", "b_09", "b_02", "b_09", "b_14", 
             "b_23", "b_04", "b_07", "b_13", "b_07", "b_13", 
             "b_07", "b_13", "b_10", "b_21", "b_10", "b_21",
             "b_01", "b_11", "b_01", "b_11", "b_20", "b_28",
             "b_28", "b_22", "b_22", "b_27", "b_22", "b_22",
             "b_27", "b_03", "b_03", "b_06" ,"b_03", "b_06", 
             "b_03", "b_06", "b_03", "b_03", "b_06", "b_19", 
             "b_29", "b_19", "b_29", "b_19", "b_29", "b_19", 
             "b_29", "b_05", "b_24" ,"b_05", "b_24", "b_05",
             "b_24", "b_05", "b_24", "b_15", "b_12", "b_15", 
             "b_12", "b_15", "b_12", "b_15", "b_12", "b_15", 
             "b_16", "b_26" ,"b_16", "b_26", "b_16", "b_26", 
             "b_16", "b_16", "b_26", "b_05", "b_12", "b_15",
             "b_16", "b_24", "b_26", "b_08", "b_06", "b_26",
             "b_14", "b_25")

species <- c("Tetrahymena thermophila",     "Tetrahymena thermophila",   
             "Tetrahymena thermophila",     "Euplotes daidaleos",
             "Euplotes daidaleos",          "Loxocephalus sp.", 
             "Euplotes daidaleos",          "Colpidium striatum",
             "Loxocephalus sp.",            "Loxocephalus sp.",
             "Dexiostoma campylum",         "Dexiostoma campylum",
             "Euplotes daidaleos",          "Euplotes daidaleos",    
             "Colpidium striatum",          "Colpidium striatum",
             "Loxocephalus sp.",            "Loxocephalus sp.", 
             "Tetrahymena thermophila",     "Tetrahymena thermophila",
             "Loxocephalus sp.",            "Loxocephalus sp.",
             "Tetrahymena thermophila",     "Tetrahymena thermophila",  
             "Colpidium striatum",          "Colpidium striatum",   
             "Dexiostoma campylum",         "Dexiostoma campylum", 
             "Stylonychia sp.",             "Euplotes daidaleos",    
             "Euplotes daidaleos",          "Staurastrum gracile",
             "Tetrahymena thermophila",     "Tetrahymena thermophila",  
             "Colpidium striatum",          "Colpidium striatum",   
             "Loxocephalus sp.",            "Loxocephalus sp.", 
             "Stylonychia sp.",             "Euplotes daidaleos",   
             "Euplotes daidaleos",          "Colpidium striatum",   
             "Colpidium striatum",          "Loxocephalus sp.",
             "Loxocephalus sp.",            "Dexiostoma campylum",    
             "Dexiostoma campylum",         "Euplotes daidaleos",    
             "Euplotes daidaleos",          "Tetrahymena thermophila",  
             "Tetrahymena thermophila",     "Colpidium striatum",   
             "Colpidium striatum",          "Loxocephalus sp.", 
             "Loxocephalus sp.",            "Euplotes daidaleos",   
             "Euplotes daidaleos",          "Staurastrum gracile", 
             "Colpidium striatum",          "Colpidium striatum",   
             "Loxocephalus sp.",            "Loxocephalus sp.",
             "Dexiostoma campylum",         "Dexiostoma campylum",  
             "Euplotes daidaleos",          "Euplotes daidaleos",    
             "Colpidium striatum",          "Colpidium striatum",  
             "Loxocephalus sp.",            "Loxocephalus sp.",
             "Dexiostoma campylum",         "Dexiostoma campylum",  
             "Stylonychia sp.",             "Euplotes daidaleos",    
             "Euplotes daidaleos",          "Staurastrum polytrichum", 
             "Staurastrum polytrichum",     "Staurastrum polytrichum",
             "Staurastrum polytrichum",     "Staurastrum polytrichum", 
             "Staurastrum polytrichum",     "Tetrahymena thermophila",   
             "Stylonychia sp.",             "Stylonychia sp.",
             "Euplotes daidaleos",          "Euplotes daidaleos") 

timeSeries_toExclude <- data.frame(
  bottle = bottles,
  species = species) %>%
  dplyr::mutate(int = interaction(bottle, species))


design_long <- design_long %>%
  dplyr::mutate(bottle.species = interaction(bottle, species)) %>%
  dplyr::filter(!(bottle.species %in% timeSeries_toExclude$int)) 

```
### TODO And here is the check

CHECK: densities2 should have the same dimensions as densties data.frame
```{r}
densities2 <- full_join(densities, design_long) # no change = everything that is supposed to be present is present
dim(densities)
dim(densities2)
```
TODO RMK densities2 has an additional field "bottle.species" which is not present in densities

### &#10003; species time series correctly removed

CHECK: data.frame "check" should be empty ()

```{r}
check <- densities %>%
  dplyr::mutate(bottle.species = interaction(bottle, species)) %>%
  dplyr::filter((bottle.species %in% timeSeries_toExclude$int)) 
check

```
RMK: OK

## And some not used code

```{r}

## Further (older) checks. not run anymore

##### Exclusion of low probability Staurastrum1 

# stau <- db_read_table(table="flowcam__algae_traits") %>%
#   dplyr::filter(species=="Staurastrum gracile",
#                 timestamp == "20210924") %>%
#   collect()
# 
# min(stau$species_probability) # good

#####  Exclusion of 20220622 25x videos

# day20220622 <- densities %>%
#   dplyr::filter(timestamp == "20220622")
# 
# table(day20220622$measurement) # good
# 
# check2 <- db_read_table(table="bemovi_mag_25__morph_mvt") %>%
#   dplyr::filter(timestamp == "20220622") %>%
#   collect()  # good
# 
# check2 <- db_read_table(table="bemovi_mag_25__morph_mvt_cropped") %>%
#   dplyr::filter(timestamp == "20220622") %>%
#   collect() # good
# 
# check2 <- db_read_table(table="bemovi_mag_25__morph_mvt_non_cropped") %>%
#   dplyr::filter(timestamp == "20220622") %>%
#   collect()  # good

##### Adding density=0 for some special cases in flowcam

# b02 <- densities %>%
#   dplyr::filter(bottle=="b_02",
#                 species %in% c("Desmodesmus armatus", "Desmodesmus clumps"))
# 
# table(b02$species, b02$day) # not implemented
# table(b02$species) # not implemented, should be 123
# 
# 
# ChlamydomonasClumps_DesmodesmusClumps <- densities %>%
#   dplyr::filter(species %in% c("Chlamydomonas clumps", "Desmodesmus clumps"))
# 
# table(ChlamydomonasClumps_DesmodesmusClumps$species, ChlamydomonasClumps_DesmodesmusClumps$bottle) # good
```
