---
title: "Reclassification"
author: "Rainer M Krug"
date: "06/05/2022"

input:
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: hide  
params:
  db: "/Volumes/Documents/RRD.Reclassification_final/LEEF.RRD.v1.8.5_4.sqlite"
  version_tag: "v1.8.5"
  base: "https://github.com/LEEF-UZH/LEEF.parameter/raw/"
  output_dir: "~/RRD.Reclassification_final/"
  archive_dir: "/Volumes/LEEF-1_archive/"
  pre_processed_folder: "/Volumes/LEEF-1_archive/LEEF.archived.data/LEEF/3.archived.data/pre_processed/"
  extracted_dir: "/Volumes/LEEF-1_archive/LEEF.archived.data/LEEF/3.archived.data/extracted/"
  toc: "/Volumes/LEEF/0.TOC/LEEF-1/toc.rds"
  cores: 7
---

# This document will run some tests on the RRD to ee if the final data cleaning has been successful

```{r}
#| label: setup
#| 

library(LEEF.analysis)
library(dplyr)
options(RRDdb = params$db)
```

# The following aspects are tested

## [x] Removing "test sampling days" and classes not of interest. Some test samplings are still in the RRD (they have sampling year 3000).
```{r}
#| label: test_1


tbls <- c(
  "bemovi_mag_16__mean_density_per_ml",
  "bemovi_mag_25__mean_density_per_ml",
  "bemovi_mag_25__mean_density_per_ml_cropped",
  "bemovi_mag_25__mean_density_per_ml_non_cropped",
  
  "bemovi_mag_16__morph_mvt",
  "bemovi_mag_25__morph_mvt",
  "bemovi_mag_25__morph_mvt_cropped",
  "bemovi_mag_25__morph_mvt_non_cropped",
  
  "flowcam__algae_density",
  "flowcam__algae_traits",
  
  "flowcytometer__flowcytometer_density"
)

sp <- c(
  "airbubbles",
  "OtherCiliate", 
  "HNA",
  "LNA", 
  "MNA",
  "Debris_and_other", 
  "Cryptomonas"
)

sp_flowcam <- c(
  "Dexiostoma",
  "Coleps_irchel",
  "Colpidium",
  "Loxocephallus",
  "Tetrahymena"
)


for (tbl in tbls){
  dat <- db_read_table(table = tbl)
  if (grep("flowcam")){
    x <- dat |>
      select(species) |> 
      distinct() |> 
      collect() |>
      filter(species %in% vars(sp_flowcam)) |>
      unlist()
    if (length(x) == 0){
      cat(tbl, ": OK", "\n")
    } else {
      cat("ERROR: ", tbl, "the following species should be filtered out: ", paste0(x, collapse = ", "), "\n")
    }
  }
  

  x <- dat |>
    select(species) |> 
    distinct() |> 
    collect() |>
    filter(species %in% vars(sp)) |>
    unlist()
  if (length(x) == 0){
    cat(tbl, ": OK", "\n")
  } else {
    cat("ERROR: ", tbl, "the following species should be filtered out: ", paste0(x, collapse = ", "), "\n")
  }
}
```

                
                
## [x] Exclusion of faulty videos from traits and recalculation of species densities (already incorporated in RRD, code not run here)
## [x] Exclusion of particles that have been classified as *Staurastrum gracile* (i.e. Staurastrum1) with a probability of less than 95% (already incorporated in RRD, code not run here and not completely up-to-date. Rainer has the complete up-to-date code)
## [x] Exclusion of 20220622 25x videos (duplicates of 20220620) from traits and setting respective densities to NA
## Adding density=0 for some special cases (algae clumps not tracked and bottle contamination. See details in section)
## [x] Manual correction of time series based on observations during the experiment
## [x] Exclusion of time series that are (almost completely) wrong classifications or only noise
## [x] Removing the linear trend in the water chemistry 

## [x] exclusion of all flowcytometer particles where FSC.A < 2 (raw FSC.A < 100)
## [x] Fix EAWAG daten (Hallo Rainer, mir ist aufgefallen, dass in der LEEF1-RRD bei den flowcytometer-Daten, die an der Eawag gemessen wurden, etwas nicht stimmt. z.B. bei timestamp "20220413" steht bei date "2022-05-17" und es gibt 3 Replikate (ich habe aber nur zwei gemessen))


# SOME TESTS ONLY
```{r}
#| label: plot
#| eval: false
#| echo: false
#| 
tn <- "bemovi_mag_16__mean_density_per_ml"
db_read_table(table = tn)
```


