---
title: "Access RRD from R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Access RRD from R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

# Install Package

The package is only on github and can be installed by using

```{r install, eval = FALSE}
if (!require("drat")) {
  install.packages("drat")
  library(drat)
}
drat::addRepo("LEEF-UZH")
install.packages("LEEF.analysis")
```

# Usage

```{r setup}
library(LEEF.analysis)
library(dplyr)
```

set the database:
```{r}
options(RRDdb = "/Volumes/LEEF/0.RRD/LEEF.RRD.sqlite")
```

**All build-in functions to read the data (i.e. `read_sql()`, `read_rrd()` (should not be used aymore), `db_read_density()` and `db_read_o2()`) access the database in READ ONLY mode and do not pose any danger of corrupting the data. Using fu nctions from the `DBI` package, can be destructive and shluld be avoided!**

## Simple reading of data
The densities can be read by using 

```{r}
db_read_density()
```

This returns an object which can be piped through `dplyr` functions and only contains a link to the database. In most cases, dplyr is creating an SQL query which is than send to the database. Data is only fetched when needed, or explicitely by using

```{r}
db_read_density() %>%
  collect()
```

Nearly all filtering is done in the SQLite database, which accelerates the acces as you can see by comparing the following, while the result is the same:

```{r}
system.time(
  x <- db_read_density() %>%
    select(timestamp, day) %>%
    distinct() %>%
    collect()
)
x
```

```{r}
system.time(
  x <- db_read_density() %>%
    collect() %>%
    select(timestamp, day) %>%
    distinct()
)
x
```

A second convenience function reads the O2 measurements:

```{r}
db_read_o2()

```

The same rules as for the function `db_read_density()` apply here.

## Using SQL syntax
You can also use SQL syntax to read from the RRD database by using the function `db_read_sql()`. This gives you a huge amount of flexibility as you can specify the sql syntax as an argument. In contrast to the functions mentioned above, this functions returns a `data.frame` of the data, and all filtering and processing after wards is done locally. For example:

```{r}
read_sql(sql = "SELECT * FROM density") %>%
    filter (as.integer(timestamp) >= as.integer(20210920)) %>%
    filter (as.integer(timestamp) <= as.integer(21000101))
```

which is the same as 
```{r}
db_read_density() %>%
  collect()
```
