---
title: "Diagnostic plots for the RRD ``r params$db``"
author: "Rainer M Krug"
date: "`r Sys.time()`"
output:
  pdf_document:
    dev: pdf
    fig_width: 10
    fig_height: 12
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
  word_document: 
    dev: png
    fig_width: 10
    fig_height: 12
params:
  db: ~/Desktop/LEEF.RRD.sqlite
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LEEF.analysis)
```
## Invocation from commandline
The report can be generated from the command line by using

```{bash info_invocation, eval = FALSE}
Rscript -e '
db <- "~/Desktop/LEEF.RRD.sqlite";
Rscript -e "library(LEEF.analysis); report_diagnostic(db);"
'
```

\pagebreak

## Check Bottles per Measurement per Timestep

This plot shows, if a `bottle` is present for the `measurement` for the timesteamps analysed. Each `measurement` is a panes. Missing dots indicate missing datapoints for the `bottle` at the `measurement` for the `timestamp`.

```{r bottles_per_timestamp}
plot_bottles_per_timestamp(params$db)
```

\pagebreak

## Number of Species per timestamp

This plot shows the 
```{r no_species_per_measurement, fig.height = 8}
plot_no_species_per_bottle_per_timestamp(params$db)
```
