---
title: "Diagnostic plots for the RRD ``r params$db``"
author: "Rainer M Krug"
date: "`r Sys.time()`"
output:
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
    toc: true
    toc_float: true
    toc_collapsed: true
  pdf_document:
    dev: pdf
    fig_width: 10
    fig_height: 12
  word_document: 
    dev: png
    fig_width: 10
    fig_height: 12
params:
  db: ~/Desktop/9.backend/LEEF.RRD.sqlite
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(LEEF.analysis)
```
## Invocation from commandline
The report can be generated from the command line by using

```{bash info_invocation, eval = FALSE}
Rscript -e "library(LEEF.analysis); db <- '~/Desktop/9.backend/LEEF.RRD.sqlite'; report_interactive();"
```

\pagebreak

## Check Bottles per Measurement per Timestep

This plot shows, if a `bottle` is present for the `measurement` for the timestamps analysed. Each `measurement` is a panes. Missing dots indicate missing datapoints for the `bottle` at the `measurement` for the `timestamp`.

```{r bottles_per_timestamp}
plot_bottles_per_timestamp(params$db)
```

\pagebreak

## Number of Species per timestamp

This plot shows the 
```{r no_species_per_measurement, fig.height = 8}
plot_no_species_per_bottle_per_timestamp(params$db)
```

\pagebreak

## Species per timestamp and measurement
Measurements are colour coded and in the order as in the legend on the right.

```{r species_per_timestamp_per_measure, fig.height = 8}
plot_species_per_timestamp_per_measure(params$db)
```

## Density of Species per bottle as measured by measurement over time

```{r dens_species, fig.height = 16}
plot_density_species_per_bottle_per_timestamp(params$db, transform_density_4throot = TRUE)
```
