---
title: "Reclassification"
author: "Rainer M Krug"
date: "1/10/2022"
output:
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = TRUE,
  warning = TRUE
)
library("LEEF.analysis")
```

# Preparation
This reclassification is based on the classifiers as in the LEEF.parameter repo in the release Reclassification_1 https://github.com/LEEF-UZH/LEEF.parameter/releases/tag/Reclassification_1.

## Set output path
```{r output_path}
output = "~/RRD.Reclassification_1/"
```


## Set Archive Directory
Make sure, that the S3 LEEF archive is mounted and you know the path to the archive as it is needed.

```{r setArchive}
archive_dir <- "~/Duck/LEEFSwift3/"
```

## Set number of cores to be used
```{r setCores}
cores <- 7
```

## Set timestamps
```{r timestamps}
timestamps <- c(20210920, 20210922, 20210924, 20210927, 20210929, 20211001, 20211004, 20211006, 20211008, 20211011, 20211013, 20211015, 20211018, 20211020, 20211022, 20211025, 20211027, 20211029, 20211101, 20211103, 20211105, 20211108, 20211110, 20211112, 20211115, 20211117, 20211119, 20211122, 20211124, 20211126, 20211129, 20211201, 20211203, 20211206, 20211208, 20211210, 20211213, 20211215, 20211217, 20211220, 20211222, 20211224, 20211227, 20211229, 20211231, 20220103, 20220105)
timestamps <- c(20210920, 20210922, 20220105)
```

# Reclassification 

## Flowcam

### Prepare Flowcam
```{r prepare_flowcam}
pdir <- tempfile()
dir.create(pdir, showWarnings = FALSE, recursive = TRUE)

class_constant <- file.path(pdir, "class_constant.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/flowcam/svm_flowcam_classifiers_18c_december2021.rds", 
  destfile = class_constant,
  mode = "wb"
)

class_increasing <- file.path(pdir, "class_increasing.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/flowcam/svm_flowcam_classifiers_increasing_trained_at_18c_december2021.rds", 
  destfile = class_increasing,
  mode = "wb"
)
```

### Classify Flowcam
```{r classify_flowcam}
out <- file.path(output, "flowcam")
if (!file.exists(out)) {
  message("Classifying flowcam...")
  system.time(
    LEEF.analysis::classify_flowcam_archive(
      archive_dir = archive_dir, 
      timestamps = timestamps, 
      algae_traits_name = "algae_traits_filtered.rds", 
      classifier_constant_name = class_constant, 
      classifier_increasing_name = class_increasing, 
      output = out,
      mc.cores = cores
    )
  )
} else {
  message(
    "Directory ", out, "exists\n",
    "skipping Flowcam."
  )
}
```

### Clean Up Flowcam
```{r cleanup_flowcam}
unlink(pdir)
rm(class_constant, class_increasing, out)
```

## Bemovi magnification 16
### Prepare Bemovi 16
```{r prepare_bemovi_16}
pdir <- tempfile()
dir.create(pdir, showWarnings = FALSE, recursive = TRUE)

class_constant <- file.path(pdir, "class_constant.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/bemovi.mag.16/svm_video_classifiers_18c_16x_december2021.rds", 
  destfile = class_constant,
  mode = "wb"
)

class_increasing <- file.path(pdir, "class_increasing.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/bemovi.mag.16/svm_video_classifiers_increasing_trained_at_18c_16x_december2021.rds", 
  destfile = class_increasing,
  mode = "wb"
)
```

### Classify `bemovi_extract.mag.16.yml`
```{r classify_bemovi_16}
out <- file.path(output, "bemovi_mag_16")
if (!file.exists(out)) {
  message("Classifying bemovi_extract.mag.16")
  system.time(
    LEEF.analysis::classify_bemovi_archive( 
      timestamps = timestamps, 
      archive_dir = archive_dir, 
      magnification = 16, 
      classifier_constant_name = class_constant, 
      classifier_increasing_name = class_increasing, 
      bemovi_extract_name = "bemovi_extract.mag.16.yml", 
      output = out,
      mc.cores = cores
    )
  )
} else {
  message(
    "Directory ", out, "exists\n",
    "Skipping 'bemovi_extract.mag.16.'"
  )
}
```

### Clean Up Bemovi 16
```{r cleanup_bemovi_16}
unlink(pdir)
rm(pdir, class_constant, class_increasing, out)
```

## Bemovi magnification 25
### Prepare Bemovi 25
```{r prepare_bemovi_25}
pdir <- tempfile()
dir.create(pdir, showWarnings = FALSE, recursive = TRUE)

class_constant <- file.path(pdir, "class_constant.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/bemovi.mag.25/svm_video_classifiers_18c_25x_december2021.rds", 
  destfile = class_constant,
  mode = "wb"
)

class_increasing <- file.path(pdir, "class_increasing.rds")
download.file(
  "https://github.com/LEEF-UZH/LEEF.parameter/raw/Reclassification_1/parameter/bemovi.mag.25/svm_video_classifiers_increasing_trained_at_18c_25x_december2021.rds", 
  destfile = class_increasing,
  mode = "wb"
)
```

### Classify `bemovi_mag.25` 
```{r classify_bemovi_25}
out <- file.path(output, "bemovi_mag_25")
if (!file.exists(out)) {
  system.time(
    LEEF.analysis::classify_bemovi_archive( 
      timestamps = timestamps, 
      archive_dir = archive_dir, 
      magnification = 25, 
      classifier_constant_name = class_constant, 
      classifier_increasing_name = class_increasing, 
      bemovi_extract_name = "bemovi_extract.mag.25.yml", 
      output = out,
      mc.cores = cores
    )
  )
  system.time(
    LEEF.analysis::classify_bemovi_archive( 
      timestamps = timestamps, 
      archive_dir = archive_dir, 
      magnification = 25, 
      classifier_constant_name = class_constant, 
      classifier_increasing_name = class_increasing, 
      bemovi_extract_name = "bemovi_extract.mag.25.non_cropped.yml", 
      output = out,
      mc.cores = cores
    )
  )
  system.time(
    LEEF.analysis::classify_bemovi_archive( 
      timestamps = timestamps, 
      archive_dir = archive_dir, 
      magnification = 25, 
      classifier_constant_name = class_constant, 
      classifier_increasing_name = class_increasing, 
      bemovi_extract_name = "bemovi_extract.mag.25.cropped.yml", 
      output = out,
      mc.cores = cores
    )
  )
} else {
  message(
    "Directory ", out, "exists\n",
    "Skipping 'bemovi_mag_25'"
  )
}
```

### Clean Up Bemovi 25
```{r cleanup_bemovi_25}
unlink(pdir)
rm(pdir, class_constant, class_increasing, out)
```
