---
title: "Update `extracted`"
author: "Rainer M Krug"
date: "06/05/2022"
input:
  html_document:
    dev: png
    fig_width: 10
    fig_height: 12
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: hide
params:
  input_dir: ~/reclassification/
---

```{r setup_reclass, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = TRUE,
  warning = TRUE
)
library(pbmcapply)
```

# Preparation
## Set input path 
The input path contains the reclassified data and was output path in the reclassification.
```{r input_path}
input <-  params$input
```

## Set Archive Directory
Make sure, that id does not point to the the S3 LEEF archive, but to a writable location containing the extracted data

```{r setArchive}
archive_dir <- "/Volumes/LEEF/"
extracted_dir <- file.path(archive_dir, "LEEF.archived.data", "LEEF", "3.archived.data", "extracted")
if (!file.exists(archive_dir)){
  stop(
    "Expected directory '", extracted_dir, "' does not exist.\n",
    "Probably not mounted?" 
  )
}
testfile <- file.path(extracted_dir, "test.tmp")
file.create(testfile)
if (!file.exists(testfile)){
  stop("The location ", testfile, " is not writable!")
}
unlink(testfile)
rm(testfile)
```

## Set number of cores to be used
```{r setCores}
cores <- 7
```

# Update `bemovi.mag.16`

## Define paths and files
```{r define_bemovi_mag_16_parameter}
source_dir <- file.path(input, "bemovi_mag_16")
source_files <- list.files(source_dir, pattern = ".rds$", recursive = TRUE)
timestamps <- sapply( strsplit(source_files, "\\."), "[[", 2)
dest_files <- basename(
  paste0(sapply( strsplit(source_files, "\\."), "[[", 1), ".", sapply( strsplit(source_files, "\\."), "[[", 3))
)
dest_files <- paste0(
  toupper(substring(dest_files, 1, 1)), 
  substring(dest_files, 2)
)

dest_rds <- file.path(
  extracted_dir, paste0("LEEF.bemovi.mag.16.bemovi.", timestamps), "5 - merged data", dest_files
)

dest_csv <- file.path(
  extracted_dir, paste0("LEEF.bemovi.mag.16.bemovi.", timestamps), gsub( "\\.rds$", ".csv", dest_files)
)
  
csv_files <- gsub("\\.rds$", ".csv", source_files)
```

## Update `.rds` files
```{r update_bemovi_mag_16_csv}
pbmcapply::pbmclapply(
  sample(length(source_files)),
  function(i){
    file.copy(
      file.path(source_dir, source_files[i]),
      dest_rds[i],
      overwrite = TRUE
    )
  }, 
  mc.preschedule = FALSE,
  mc.cores = 2
)
```

## Update `.csv` files

```{r update_bemovi_mag_16_csv}
pbmcapply::pbmclapply(
  sample(length(source_files)),
  function(i){
    write.csv(
      readRDS(file.path(source_dir, source_files[i])),
      dest_csv[i]
    )
  }, 
  mc.preschedule = FALSE,
  mc.cores = cores
)
```



# Update `bemovi.mag.25`

## Define paths and files
```{r define_bemovi_mag_25_parameter}
source_dir <- file.path(input, "bemovi_mag_25")
source_files <- list.files(source_dir, pattern = ".rds$", recursive = TRUE)
timestamps <- sapply( strsplit(source_files, "\\."), "[[", 2)
dest_files <- basename(
  paste0(sapply( strsplit(source_files, "\\."), "[[", 1), ".", sapply( strsplit(source_files, "\\."), "[[", 3))
)
dest_files <- paste0(
  toupper(substring(dest_files, 1, 1)), 
  substring(dest_files, 2)
)

dest_rds <- file.path(
  extracted_dir, paste0("LEEF.bemovi.mag.25.bemovi.", timestamps), "5 - merged data", dest_files
)

dest_csv <- file.path(
  extracted_dir, paste0("LEEF.bemovi.mag.25.bemovi.", timestamps), gsub( "\\.rds$", ".csv", dest_files)
)
  
csv_files <- gsub("\\.rds$", ".csv", source_files)
```

## Update `.rds` files
```{r update_bemovi_mag_25_rds}
pbmcapply::pbmclapply(
  sample(length(source_files)),
  function(i){
    file.copy(
      file.path(source_dir, source_files[i]),
      dest_rds[i],
      overwrite = TRUE
    )
  }, 
  mc.preschedule = FALSE,
  mc.cores = 2
)
```

## Update `.csv` files

```{r update_bemovi_mag_25_csv}
pbmcapply::pbmclapply(
  sample(length(source_files)),
  function(i){
    write.csv(
      readRDS(file.path(source_dir, source_files[i])),
      dest_csv[i]
    )
  }, 
  mc.preschedule = FALSE,
  mc.cores = cores
)
```

# Update `flowcam`
## Define paths and files
```{r define_flowcytometer_parameter}
source_dir <- file.path(input, "reclassification flowcam_b_02_20220128_30000000", "flowcam_b_02_20220128_30000000")
source_files <- list.files(source_dir, pattern = ".rds$", recursive = TRUE)
timestamps <- sapply( strsplit(source_files, "\\."), "[[", 2)
dest_files <- basename(
  paste0(sapply( strsplit(source_files, "\\."), "[[", 1), ".", sapply( strsplit(source_files, "\\."), "[[", 3))
)

dest_csv <- file.path(
  extracted_dir, paste0("LEEF.fast.flowcam.", timestamps), gsub( "\\.rds$", ".csv", dest_files)
)
  
csv_files <- gsub("\\.rds$", ".csv", source_files)
```

## Update `.csv` files

```{r update_flowcytometer_csv}
pbmcapply::pbmclapply(
  sample(length(source_files)),
  function(i){
    write.csv(
      readRDS(file.path(source_dir, source_files[i])),
      dest_csv[i]
    )
  }, 
  mc.preschedule = FALSE,
  mc.cores = cores
)
```


# Re-create overlays


```{r overlays}
stop("TODO")

overlays_from_folders <- function(
    traj_data_file,
    avi_dir,
    bemovi_extract_yml_file,
    temp_overlay_folder,
    overlay_folder,
    overlay_type = "both",
    label = "species",
    ffmpeg = "ffmpeg",
    font_size = 24,
    circle_size = 120,
    crf = 23,
    gamma = 2,
    mc_cores = 1
)

```
